Brother, Can You Spare a Manufacturing Job? How Voters React to Deindustrialization

### 2021-12-12 Final Draft/Final Draft.Rmd
pushing updates to final draft

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(rticles)
library(tidyverse)
library(stargazer)
library(sandwich)
library(lmtest)
library(knitr)
library(kableExtra)
library(readxl)
library(scales)
library(tigris)

knitr::opts_chunk$set(fig.pos = "!H", out.extra = "")
```

@@

\begin{figure} \label{counterfactual}
\caption{Change in Democratic Vote Share Assuming 25th Percentile of Manufacturing Job Losses}
```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center"}

@@

>>>>

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(rticles)
library(tidyverse)
library(stargazer)
library(sandwich)
library(lmtest)
library(knitr)
library(kableExtra)
library(readxl)
library(scales)
library(tigris)
library(dplyr)
knitr::opts_chunk$set(fig.pos = "!H", out.extra = "")
```

@@

\begin{figure} \label{counterfactual1}
\caption{Change in Democratic Vote Share Assuming 25th Percentile of Manufacturing Job Losses}
```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center"}

@@

\begin{figure} \label{counterfactual2}
\caption{Clinton Electoral College Votes}
```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center"}

# load map
simulation_results <- readRDS("../counterfactual_simu_results.rds")
num_sims <- 1000

summary <- simulation_results %>%
  group_by(ptile) %>%
  arrange(trump_votes_cf) %>%
  summarize(median_result = clinton_votes_cf[row_number() == (num_sims/2)],
            lower = clinton_votes_cf[row_number() == (num_sims/40)],
            upper = clinton_votes_cf[row_number() ==(num_sims- (num_sims/40))])

# plot distribution and each percentile

# first plot CI
ggplot(summary, aes(ptile, median_result)) + 
  geom_point() +
  geom_errorbar(aes(ymin = lower, ymax = upper),
                color = "blue") +
  geom_hline(yintercept = 270, color = "red") +
  theme_bw() +
  ylab("Outcome: Clinton Electoral College Votes\n") +
  xlab("Input Assumption: Percentile of Manufacturing Layoffs\n") +
  ggtitle("Counterfactual Presidential Election Simulation Results")

\begin{figure} \label{counterfactual3}
\caption{Clinton Winning Freq}
```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center"}

library(dplyr)
library(ggplot2)
summary2 <- simulation_results %>%
  mutate(hil_wins = case_when(clinton_votes_cf > 270 ~ 1,
                              TRUE ~ 0)) %>%
  group_by(ptile) %>%
  summarize(perc_wins =  sum(hil_wins)/n())

ggplot(summary2, aes(ptile, perc_wins)) + 
  geom_col(fill = "#4287f5")  +
  theme_bw() +
  ylab("Outcome: Frequency of Clinton Winning\nIn 1000 Simulations") +
  xlab("Input Assumption: Percentile of Manufacturing Layoffs\n") +
  ggtitle("Counterfactual Presidential Election Simulation Results")

### 2021-12-12 Final Draft/Final-Draft.tex
pushing updates to final draft

This coefficient is still somewhat difficult to interpret, and made
increasingly so by the winner-take-all system by which U.S. Electoral
College votes are allocated. As an alternative perspective, we examined
a range of counterfactual scenarios, in which counties experienced job
losses

\begin{figure} \label{counterfactual}
\caption{Change in Democratic Vote Share Assuming 25th Percentile of Manufacturing Job Losses}

\begin{center}\includegraphics{Final-Draft_files/figure-latex/unnamed-chunk-6-1} \end{center}
\begin{figurenotes}
Gain or loss of national manufacturing jobs, divided by total national workforce.
\end{figurenotes}
\end{figure}

XXXXXXXXXXXXXXXXXXXXXX EXPLAIN COUNTERFACTUAL

@@

\begin{center}\includegraphics{Final-Draft_files/figure-latex/unnamed-chunk-8-1} \end{center}
\begin{figurenotes}
"Stuff here"
\end{figurenotes}
\end{figure}

@@

\begin{center}\includegraphics{Final-Draft_files/figure-latex/unnamed-chunk-9-1} \end{center}

>>>>

This coefficient is still somewhat difficult to interpret, and made
increasingly so by the winner-take-all system by which U.S. Electoral
College votes are allocated. As an alternative perspective, we examined
a range of counterfactual scenarios, in which counties experienced job
losses XXXXXXXXXXXXXXXXXXXXXX EXPLAIN COUNTERFACTUAL

\begin{figure} \label{counterfactual1}
\caption{Change in Democratic Vote Share Assuming 25th Percentile of Manufacturing Job Losses}

\begin{center}\includegraphics{Final-Draft_files/figure-latex/unnamed-chunk-6-1} \end{center}
\end{figure}

\begin{figure} \label{counterfactual2}
\caption{Clinton Electoral College Votes}

\begin{center}\includegraphics{Final-Draft_files/figure-latex/unnamed-chunk-7-1} \end{center}
\end{figure}

\begin{figure} \label{counterfactual3}
\caption{Clinton Winning Freq}

\begin{center}\includegraphics{Final-Draft_files/figure-latex/unnamed-chunk-8-1} \end{center}
\end{figure}

@@

\begin{center}\includegraphics{Final-Draft_files/figure-latex/unnamed-chunk-10-1} \end{center}
\begin{figurenotes}
"Stuff here"
\end{figurenotes}
\end{figure}

@@

\begin{center}\includegraphics{Final-Draft_files/figure-latex/unnamed-chunk-11-1} \end{center}
